%%% Seznam použité literatury je zpracován podle platných standardů. Povinnou citační
%%% normou pro bakalářskou práci je ISO 690. Jména časopisů lze uvádět zkráceně, ale jen
%%% v kodifikované podobě. Všechny použité zdroje a prameny musí být řádně citovány.

\def\bibname{Seznam použité literatury}
\addcontentsline{toc}{chapter}{\bibname}

\begin{thebibliography}{99}
%\addcontentsline{toc}{chapter}{\bibname}

%MUNROE, Randall. Random Number. In: XKCD: A webcomic of
%romance, sarcasm, math and language [online]. 2010
%[cit. 2011-10-04]. Dostupne z: ´ http://xkcd.com/221/

\bibitem{jurafsky08}
  {\sc JURAFSKY,} Dan a James {\sc H. MARTIN}. 
  \emph{Speech and language processing: an introduction to natural language processing, computational linguistics, and speech recognition}. 2nd ed. Upper Saddle River: Pearson Education, 2008. ISBN 978-0-13-187321-6. 
  
\bibitem{ghaoui}
{\sc GHAOUI,} A.; F. {\sc YVON}; C. {\sc MOKHBEL}, G. {\sc CHOLLET} (2005), \emph{ On the use of morphological constraints in n-gram statistical language model.}, in 'INTERSPEECH' , ISCA, p. 1281-1284.  


\bibitem{wakita}
{\sc WAKITA}, Yumi, {\sc KAWAI} Jun, {\sc IID} Hitoschi, \emph{An Evaluation Of Statistical Language Modeling For Speech Recognition Using a Mixed Category of Both Words and Parts-Of-Speech}
  [online] [cit. 2013-05-04].
  Dostupné z: \url{http://www.asel.udel.edu/icslp/cdrom/vol1/974/a974.pdf}  


\bibitem{geutner}
{\sc GEUTNER}, Petra. \emph{Fuzzy class rescoring: a part-of-speech language model.} In George Kokkinakis, Nikos Fakotakis, Evangelos Dermatas, editors, Fifth European Conference on Speech Communication and Technology, EUROSPEECH 1997, Rhodes, Greece, September 22-25, 1997. ISCA, 1997. 


\bibitem{popovic}
{\sc POPOVIĆ}, Maja. \emph{Proceedings of the Sixth Workshop on Statistical Machine Translation. Workshop on Statistical Machine Translation (WMT-11)}, Association for Computational Linguistics, 2011 p. 104-107

\bibitem{fraser12}
  {\sc FRASER,} Alexander, Marion {\sc WELLER} a Cahilly Fabienne {\sc CAP}. \emph{Modeling Inflection and Word-Formation in SMT} 
  [online]. 2012
  [cit. 2013-05-04].
  Dostupné z: \url{http://eprints.pascal-network.org/archive/00009510/01/morphgen_hmm.pdf}  

\bibitem{ruokolainen}
\sc{RUOKOLAINEN}, Teemu, Tanel ALUMÄE, Marcus DOBRINKAT. \emph{Using Dependency Grammar Features in Whole Sentence Maximum Entropy}, Language Model for Speech Recognition,
 [online]. 2010
  [cit. 2013-05-03].
  Dostupné z: \url{http://www.pinview.eu/files/Ruokolainen2010.pdf}  

\bibitem{amaya}
{\sc AMAYA}, Fredy and José Miguel {\sc BENEDÍ}, \emph{Improvement of a Whole Sentence Maximum Entropy Language Model using grammatical features},
Proceedings of the 39th Annual Meeting on Association for Computational Linguistics, 2001.

\bibitem{turing}
{\sc GOOD} I. J. \emph{The Population Frequencies of Species and the Estimation of Population Parameters} Biometrika, Vol. 40, No. 3/4. (Dec., 1953), pp. 237-264.

\bibitem{emal}
{\sc SINGH} Ajit, \emph{The EM Algorithm}
[online]. 2005
  [cit. 2013-05-05].
  Dostupné z: \url{http://www.cs.cmu.edu/~awm/10701/assignments/EM.pdf}  



\bibitem{srilm}
\sc{SRILM} - The SRI Language Modeling Toolkit
 [online].
  [cit. 2013-05-01].
  Dostupné z: \url{http://www.speech.sri.com/projects/srilm/}  
  
\bibitem{chen}
{\sc CHEN} F. Stanley, Joshua {\sc GOODMAN} \emph{ An Empirical Study of Smoothing Techniques for Language Modeling}
 [online]. 1998
  [cit. 2013-05-02].
  Dostupné z: \url{http://www.ee.columbia.edu/~stanchen/papers/h015a-techreport.pdf}  
  
\bibitem{gis}
{\sc DARROCH}, J. N. and {\sc D. RATCLIFF} \emph{Generalized Iterative Scaling for Log-Linear Models} Ann. Math. Statist. Volume 43, Number 5 (1972), 1470-1480.  

\bibitem{lbfgs}
{\sc LIU}, Dong C., Jorge {\sc NOCEDAL} \emph{ ON THE LIMITED MEMORY BFGS METHOD FOR
LARGE SCALE OPTIMIZATION}
 [online]. 1989
  [cit. 2013-04-09].
  Dostupné z: \url{http://users.eecs.northwestern.edu/~nocedal/PDFfiles/limited-memory.pdf}

\bibitem{lzhang}
{\sc ZHANG}, Le. \emph{Maximum Entropy Modeling Toolkit for Python and C++}
[online]. 2004
  [cit. 2013-02-03].
  Dostupné z: \url{http://homepages.inf.ed.ac.uk/lzhang10/software/maxent/manual.pdf}
  
\bibitem{chen2}
{\sc CHEN} S. F. \emph{Performance prediction for exponential language models} in Proceedings of HLT-NAACL, Boulder, Colorado, 2009, pp. 450–458.  

\bibitem{tanel}
{\sc ALUMÄE} Tanel, Mikko {\sc KURIMO}. \emph{Efficient Estimation of Maximum Entropy Language Models with {N}-gram features: an {SRILM} extension}
[online]. 2010
  [cit. 2013-02-03].
  Dostupné z: \url{http://www.phon.ioc.ee/dokuwiki/lib/exe/fetch.php?media=people:tanel:interspeech2010.pdf}

\bibitem{treetagger}
{\sc SCHMID}. TreeTagger - a language independent part-of-speech tagger
[online].
  [cit. 2013-03-09].
  Dostupné z: \url{http://www.cis.uni-muenchen.de/~schmid/tools/TreeTagger/}
 
\bibitem{morphisto}
University of Stuttgart, \emph{morphisto - FST-based Morphological Analyzer for German}
[online].
  [cit. 2013-05-09].
  Dostupné z: \url{https://code.google.com/p/morphisto/}
  
\bibitem{parzu}
{\sc SENNRICH} \emph{ ParZu - The Zurich Dependency Parser for German (formerly known as Pro3GresDE)}
[online].
  [cit. 2013-05-07].
  Dostupné z: \url{https://github.com/rsennrich/ParZu}

\bibitem{tager}
{\sc ALLAUZEN} A., {\sc BONNEAU-MAYNARD} \emph{Training and evaluation of POS taggers on the French MULTITAG corpus}
[online] 2008.
  [cit. 2013-05-11].
  Dostupné z: \url{http://www.lrec-conf.org/proceedings/lrec2008/pdf/856_paper.pdf}

\bibitem{trec}
{\sc TREC 2006} \emph{The Fifteenth Text REtrieval Conference Proceedings}
[online] 2006.
  [cit. 2013-05-22].
  Dostupné z: \url{http://trec.nist.gov/pubs/trec15/appendices/CE.MEASURES06.pdf}
  



\bibitem{bojar}
{\sc BOJAR}, Ondřej. \emph{Čeština a strojový překlad: strojový překlad našincům, našinci strojovému překladu.} Praha: Ústav formální a aplikované lingvistiky, c2012, vi, 162 s. Studies in computational and theoretical linguistics. ISBN 978-80-904571-4-0.
 



  


 
  

\end{thebibliography}
 

